Quantitative, Multispecies Monitoring at a Continental Scale

### 2025-02-25 Priors table.tex

\begin{table}[h]
    \centering
    \begin{tabular}{lll}
         & \textbf{Description} & \textbf{Prior} \\
&Data & \\
\hline
$K$ & known DNA concentration from qPCR standards in ln(copies/$\mu$L) & - \\
$Z$ & qPCR amplification (yes=1; no=0) & - \\
$Y$ & qPCR cycle threshold (Ct) & - \\
$R$ & metabarcoding number of reads & - \\
$T$ & total number of reads for all S species & - \\
$N_{PCR}$ & number of metabarcoding PCR cycles & - \\
$L$ & known DNA concentration from mock commuinties in ln(copies/$\mu$L) & - \\
$V$ & volume filtered and aliquote dilution offset & -\\
$I$ & aliquote dilution factor & -\\

>>>>

\begin{table}[h]
    \centering
    \begin{tabular}{lll}
         & \textbf{Description} & \textbf{Prior} \\
&Data & \\
\hline
$K$ & known DNA concentration from qPCR stsandards in ln(copies/$\mu$L) & - \\
$Z$ & qPCR amplification (yes=1; no=0) & - \\
$Y$ & qPCR cycle threshold (Ct) & - \\
$R$ & metabarcoding number of reads & - \\
$T$ & total number of reads for all S species & - \\
$N_{PCR}$ & number of metabarcoding PCR cycles & - \\
$L$ & known DNA concentration from mock commuinties in ln(copies/$\mu$L) & - \\
$V$ & volume filtered and aliquote dilution offset & -\\
$I$ & aliquote dilution factor & -\\
